\documentclass{article}
\usepackage[utf8]{inputenc}

\title{DMSP_Requirements}
\author{lukas }
\date{November 2019}

\begin{document}


\section{Introduction}

Operation

TL-1 The engine shall be able to provide sufficient thrust for completion of the mission profile including a safety margin of 5\%.

TL-2 The engine shall be re-ignitable at least 250 times.

TL-3 The engine shall have a service life time of at least 25 missions or 5 years in orbit.

TL-4 The engine's ignition and functional reliability shall be higher than 99,5\%.

Environment

TL-5 The engine shall be able to withstand the launch phase.

TL-6 The engine shall be able to operate in vacuum.

TL-7 The engine shall be able to operate in an ambient temperature range of 1K to 5K.

TL-8 The engine shall be able to withstand the temperature gradients resulting from areas turned towards or away from the sun.

TL-9 The engine shall be able to sustain space-related radiation throughout it's complete life time.

Vehicle

TL-10 The vehicle shall offer an interface to the engine which is able to sustain maximum loads at a technical safety of 1,2.

TL-11 The vehicle shall be refuelable between missions.

TL-12 The vehicle shall be able to perform aerobreak maneauvers in earth's atmosphere.

TL-13 The vehicle shall be able to manipulate it's flight path in earth's atmosphere using non-propulsive flight control systems.

TL-14 The vehicle shall remain within the ARIANE 5 payload launch capabilities to LEO.

TL-15 The vehicle shall be able to withstand debris impact of objects under 1cm of diameter with a maximum relative speed of 15km/s.

TL-16 The vehicle shall be able to remain on it's guided trajectory with less than 0,1\% deviation.

TL-17 The vehicle shall be able to manipulate it's trajectory using attitude control systems.

TL-18 The vehicle shall be able to capture a satellite spinning uncontrolled at up to 1 rotation per second.

TL-19  The vehicle shall be continuously able to send and receive telemetry data at intervals of 0,5 seconds.

TL-20 The vehicle shall be able to control every subsystem's temperature in order to keep it within the operating range.

    SL-201 The batteries shall be maintained within an operating temperature range of 0 - 30 degrees celsius.
    
    SL-202 The board computer shall be maintained within an operating temperature range of -55 - 125 degrees celsius.
    
    SL-203 The telecommunications equipment shall be maintained within an operating temperature range of -30 - 70 degrees celsius.

TL-21 Single components and sub-systems should be redundantly available if they impose a single point of failure.

\end{document}
