\documentclass{article}
\usepackage[utf8]{inputenc}

\title{DMSP Requirements}
\author{lukas }
\date{November 2019}

\begin{document}

\maketitle

\section{Introduction}

Operation

TL-1 The engine shall be able to provide sufficient thrust for completion of the mission profile including a safety margin.

TL-2 The engine shall be re-ignitable at least 1000 times.

TL-3 The engine shall have a service life time of at least 100 missions or 25 years in orbit.

TL-4 The engine's ignition and functional reliability shall be higher than 99,5$\%$.

Environment

TL-5 The engine shall be able to withstand the launch phase.

TL-6 The engine shall be able to operate in vacuum.

TL-7 The engine shall be able to operate in an ambient temperature range of 1K to 5K.

TL-8 The engine shall be able to withstand the temperature gradients resulting from areas turned towards or away from the sun.

TL-9 The engine shall be able to sustain space-related radiation throughout it's complete life time.

Vehicle

TL-10 The engine shall be the main propulsion system of a GEO satellite recovery vehicle.

TL-11 The vehicle shall be refuelable between missions.

TL-12 The vehicle shall be able to perform aerobreak maneauvers in earth's atmosphere.

TL-13 The vehicle shall be able to manipulate it's flight path in earth's atmosphere using non-propulsive flight control systems.

TL-14 The vehicle shall remain within the ARIANE 5 payload launch capabilities to LEO.

TL-15 The vehicle shall be able to withstand debris impact of objects under 1cm of diameter with a maximum relative speed of 15km/s

TL-16 The vehicle shall be able to remain on it's guided trajectory with less than 0.1$\%$ deviation.
\end{document}
